Agenda diversity and coverage bias: A quantitative approach to the agenda-setting theory

### 2018-07-13 paper_balen.tex
Version para subir al arxiv

The Agenda Setting theory provides a conceptual framework in order to understand the role played by the Mass Media in a society. Within this framework, the Media are not only capable to make people think about certain issues, but also to make how to think about them. When this is accomplished,  we say that the media set the agenda. 
In this work we study the agenda of Argentinian newspapers in comparison with public's interests through a quantitative approach by performing topic detection over the news, identifying the main topics covered and their evolution over time. We measure Agenda's diversity as a function of time using Shannon's entropy and difference between Agendas using Jensen-Shannon's distance. We found that the Public Agenda is less diverse than the Media Agenda, and we are also capable to detect periods of time where coverage of certain issues are biased (coverage bias). \\

>>>>

The mass media play a fundamental role in the formation of public opinion, either by defining the topics of discussion or by making a degree of emphasis on certain issues. Directly or indirectly, people get informed by consuming news from the media. But which is the dynamic of the agenda and how the people becomes interested in the different topics of the agenda? The Agenda Setting theory provides a conceptual framework in order to understand the role played by the mass media in public opinion formation, but the previous questions can not be answered without proper quantitative measures of agenda's dynamic and public attention. In this work we study the agenda of Argentinian newspapers in comparison with public’s interests through a quantitative approach by performing topic detection over the news, identifying the main topics covered and their evolution over time. We measure Agenda’s diversity as a function of time using Shannon’s entropy and difference between Agendas using Jensen-Shannon’s distance. We found that the Public Agenda is less diverse than the Media Agenda, and we are also capable to detect periods of time where coverage of certain issues are biased (coverage bias).\\
